A multi-dimensional extension of the Lightweight Temporal Compression method

### 2018-10-11 paper.tex
result

>>>>

\todo{ update }
try using difference data set to measure compression radio, Error 
and energy usage. The numerical value presented below, is the 
average value in 5 seconds. The current electric current for Neblina 
without transmit is ***. we received 4000 data for human running and 
walking in 200Hz. Because of the limite RAM, for energy test, we only
could save 400 static data into Neblina. We make 400 data run as a circle.
For walking, one time swing arm need 1.2 second. Every 400 data must have 1 arm swing.
change epsilon in order to decrease compression radio, measuring energy consumption.

\todo {running}
If it's possible to save more static data?
